Model

### 2019-05-05 stats/model.Rmd
restrict prior range to more sensible range; rename parameters for clarity

  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
  //var speakerOptimality = uniformDrift({a: -5, b: 5, width: 0.2})

  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
  // conceptually it might not make sense to have two sigmas, but maybe it does
  // intercept sigma probably will be smaller than slope sigma
  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})

@@

    var sem_slope_item = gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5})
    var sem_int_item = gaussianDrift({mu: sem_int_global, sigma: item_int_sigma, width: 0.5})

    // var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
    // var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})

@@

@@

    query.add(["parameter","items", cndtn], [sem_int_item, sem_slope_item])

@@

  query.add(["parameter","parameters","speaker_optimality"], [so_int, so_slope])
  query.add(["parameter","parameters", "global_sem"], [sem_int_global, sem_slope_global])
  query.add(["parameter","sigma", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])

>>>>

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
    slope: uniformDrift({a: -2, b: 2, width: 0.5})
  }

  var globalLineParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 1}),
    slope: uniformDrift({a: -3, b: 3, width: 1})
  }

  var itemVariability = {
    intercept: uniformDrift({a: 0, b: 1, width: 0.2}),
    slope: uniformDrift({a: 0, b: 1, width: 0.2})
  }

  // conceptually it might not make sense to have two sigmas, but maybe it does
  // intercept sigma probably will be smaller than slope sigma
  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})

@@

      var itemLineParameters = {
        intercept: gaussianDrift({
          mu: globalLineParameters.intercept, 
          sigma: itemVariability.intercept, 
          width: 0.5
        }),
        slope: gaussianDrift({
          mu: globalLineParameters.slope, 
          sigma: itemVariability.slope, 
          width: 0.5
        })
      }

@@

      var sem_knowledge = logistic(itemLineParameters.intercept + 
          itemLineParameters.slope * age)

      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age

@@

    query.add(["parameter","items", cndtn], [itemLineParameters.intercept, itemLineParameters.slope])

@@

  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
